\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts,bm}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{markdown}
\markdownSetup{
	renderers = {
		link     = {#1},        % Render a link as the link label.
		emphasis = {\emph{#1}}, % Render emphasis using `\emph`.
	}
}
\usepackage{minted} % code listing
\usemintedstyle{trac}

\definecolor{LightGray}{gray}{0.95}

\newtheorem{definition}{Definition}

\setlength{\parindent}{0pt}

\title{COMP550 Natural Language Processing\\Assignment 3}
\author{Jonathan Guymont}

\begin{document}

\maketitle

\section*{Question 1}

(a) 

\begin{equation}
\begin{split}
	(\lambda x. xx)(\lambda y. yx) z 
	=& (\lambda y. y x) (\lambda y. y x) z\\
	=& (\lambda y. y x) xz \\
	=& xxz \\
\end{split}
\end{equation}

\begin{equation}
\begin{split}
	(\lambda uvw.wvu)aa(\lambda pq. q) z 
	=& (\lambda pq. q) aa\\
	=& a \\
\end{split}
\end{equation}

\begin{equation}
\begin{split}
	[(\lambda v.vv)(\lambda u. u)] [(\lambda v.v)(\lambda v.w)]
	=& [(\lambda u.u)(\lambda u. u)](\lambda v.w)\\
	=&  (\lambda u.u)(\lambda v. w)\\
	=& (\lambda v. w)
\end{split}
\end{equation}

(b) \\
\texttt{DET -> no}    \\ 
\texttt{V -> hates} \\

The word \textit{no} is used to say none of the object with characteristic $P$ have the attribute $Q$ (e.g. no tomatoes are pink, there is no human on mars,...). So it can be read has \textit{for all $x$ such that $x$ is $P$, $x$ is not $Q$}.  
\[
	\lambda P. \lambda Q. \forall x. P(x) \rightarrow  \neg Q(x)
\]

When the verb \textit{hates} is used, there is an event $e$:\textit{something is hated}, the event need a \textit{hater} $z$, and a \textit{hatee} $x$
\[
	\lambda w. \lambda z. w[\forall x. \exists e~ hates(e) \land hater(e,z) \land hatee(e, x)]
\]
\textbf{Parsing tree.}\\
Let \texttt{A}$\equiv \lambda z.\exists e. ~hates(e)\land hater(e, z) \land hatee(e, COMP550)$\\

The semantis of \texttt{S} is given by
\begin{equation}
\begin{split}
[\lambda Q.& \forall x. student(x)\rightarrow \neg Q(x)](A)\\
=& \lambda Q. \forall x. student(x)\rightarrow \neg A(x)\\
=& \lambda Q. \forall x. student(x)\rightarrow \neg [\lambda z.\exists e. ~hates(e)\land hater(e, z) \land hatee(e, COMP550)](x)\\
=& \lambda Q. \forall x. student(x)\rightarrow \neg [\exists e. ~hates(e)\land hater(e, X) \land hatee(e, COMP550)]\\
\end{split}
\end{equation}

\texttt{S}$~~~~<\lambda Q. \forall x. student(x)\rightarrow \neg \exists e. ~hates(e)\land hater(e, X) \land hatee(e, COMP550)>$\\
\texttt{S -> NP VP}\\

\texttt{NP}$~~~~<\lambda P. \lambda Q. \forall x. student(x)\rightarrow \neg Q(x)>$\\
\texttt{NP -> DET N}\\

\texttt{DET}$~~~~<\lambda P. \lambda Q. \forall x. P(x)\rightarrow \neg Q(x)>$\\
\texttt{DET -> no}\\

\texttt{N}$~~~~<\lambda x. student(x)>$\\
\texttt{N-> student}\\

\texttt{VP}$~~~~<\lambda z.\exists e. ~hates(e)\land hater(e, z) \land hatee(e, COMP550)>$\\
\texttt{VP -> V PN}\\

\texttt{V}$~~~~<\lambda w. \lambda z. w[\forall x. \exists e~ hates(e) \land hater(e,z) \land hatee(e, x)]>$\\
\texttt{V -> hates}\\

\texttt{PN}$~~~~<\lambda X. x(COMP550)>$\\
\texttt{PN -> COMP550}\\

(c) The representation of wants is
\[
	\exists e wants(e) \land wanter(e, s_1) \land wantee(e, s_2)
\]

\textbf{First interpretation}: Start with the predicate \textit{there is an exam $y$ that is wanted by $s_1$} and then \textit{for each student $x$ negate this predicate over $s_1$}

\begin{equation}
\begin{split}
	(\lambda Q.& \exists y. exam(y) \land Q(y))(\lambda s_2. \exists e. wants(e) \land wanter(e, s_1) \land wantee(e, s_2))\\ 
	=& \exists y. exam(y) \land \exists e. want(e) \land wanter(e, s_1) \land wantee(e, y) 
\end{split}
\end{equation}

\begin{equation}
\begin{split}
(\lambda Q.& \forall x. student(x)\rightarrow \neg Q(x))(\lambda s_1. \exists y. exam(y) \land \exists e. want(e) \land wanter(e, s_1) \land wantee(e, y)) \\
=& \forall x. student(x) \rightarrow \neg [\lambda s_1.\exists y. exam(y) \land \exists e. want(e) \land wanter(e, s_1) \land wantee(e, y)](x) \\
=& \forall x. student(x) \rightarrow \neg \exists y. exam(y) \land \exists e. want(e) \land wanter(e, x) \land wantee(e, y) \\
\end{split}
\end{equation}

Interpretation 1: There is no exam  anywhere that any students want.\\

\textbf{Second interpretation}: Start with \textit{There is an object $s_2$ that is not wanted by any student $x$} and then replace this object by an exam $y$ that can have the property $Q$ (of not being wanted in that case).

\begin{equation}
\begin{split}
(\lambda Q.& \forall x. student(x)\rightarrow \neg Q(x))(\lambda s_1. \exists e. want(e) \land wanter(e, s_1) \land wantee(e, s_2)) \\
=& \forall x. student(x) \rightarrow \neg (\exists e. want(e)\land wanter(e, x) \land wantee(e, s_2)) \\
\end{split}
\end{equation}

\begin{equation}
\begin{split}
(\lambda Q.& \exists y. exam(y) \land Q(y))(\lambda s_2. \forall x. student(x) \rightarrow \neg (\exists e. want(e)\land wanter(e, x) \land wantee(e, s_2)))\\ 
=& (\exists y. exam(y)) \land [\forall x. student(x) \rightarrow \neg (\exists e. want(e)\land wanter(e, x) \land wantee(e, y))]
\end{split}
\end{equation}

\textbf{Interpretation 2}: There is a particular exam that no student want. 











\end{document}
